An Adolescent Mini-Neptune in the Kepler Field

### 2021-07-30 paper/ms.tex
rotation periods

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f15a.pdf}
			\includegraphics[width=0.49\textwidth]{TEMP_Prot_vs_BpmRp.png}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is $35\pm15$\,Myr old.}  {\it Left:} HR diagram of 
    the \cn, IC\,2602 ($\approx35$\,Myr), the Pleiades ($\approx 115$\,Myr), and the field.
    The \cn\ and IC\,2602 are approximately the same isochronal age.
    {\it Right:} TESS and Kepler rotations periods and dereddened Gaia
    colors, with the Pleiades
    \citep[125\,Myr;][]{rebull_rotation_2016a} and Praesepe
    \citep[650\,Myr;][]{douglas_poking_2017} shown for reference.
    Stars of a given color (mass) move up through time due to magnetic
    braking.  The \cn\ has a 40 Myr gyrochronal age, as calibrated
    against the LDB-age of IC\,2602.  {\bf todo: caption improve. fix
    figures.}.
   \label{fig:age}
	}
\end{figure*}

@@

following {\bf procedure X,Y,Z}.

@@

\subsection{Rotation Periods}
{\bf Jason Curtis todo}
We collected the previously measured
{\bf XXX} Kepler rotation periods (CITEP MCQUILLAN2014), and measured
{\bf YYY} new stellar rotation periods for cluster members observed by
TESS.  We also performed an isochronal analysis.  The results are
shown in Figure~\ref{fig:age}.  From the ensemble perspective, which
provides the strongest constraints (SEE CITET SODERBLOM 2014), the age
of the star is $XX \pm YY$\,Myr.  Individual measurements of the
star's rotation period and lithium abundance corroborate this
conclusion.

@@

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f15a.pdf}
			\includegraphics[width=0.49\textwidth]{f15b.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is $35\pm15$\,Myr old.}  {\it Top:} HR diagram of 
    the \cn, IC\,2602 ($\approx35$\,Myr), the Pleiades ($\approx 115$\,Myr), and the field.
    The right panel provides a closer view of stars on the
    pre-main-sequence.
    The \cn\ and IC\,2602 are approximately the same isochronal age.
    {\it Bottom:} TESS and Kepler rotations periods and dereddened Gaia
    colors, with the Pleiades
    \citep[125\,Myr;][]{rebull_rotation_2016a} and Praesepe
    \citep[650\,Myr;][]{douglas_poking_2017} shown for reference.
    Stars of a given color (mass) move up through time due to magnetic
    braking.  The \cn\ has a 40 Myr gyrochronal age, as calibrated
    against the LDB-age of IC\,2602.  {\bf todo: caption improve.}.
   \label{fig:age}
	}
\end{figure*}

@@

%FIXME FIXME TODO TODO get the ages measured

@@

\subsection{Rotation Periods}
%FIXME TODO REFERENCE LOWER PANELS
{\bf Jason Curtis todo}
We collected the previously measured
{\bf XXX} Kepler rotation periods (CITEP MCQUILLAN2014), and measured
{\bf YYY} new stellar rotation periods for cluster members observed by
TESS.  We also performed an isochronal analysis.  The results are
shown in Figure~\ref{fig:age}.  From the ensemble perspective, which
provides the strongest constraints (SEE CITET SODERBLOM 2014), the age
of the star is $XX \pm YY$\,Myr.  Individual measurements of the
star's rotation period and lithium abundance corroborate this
conclusion.

For photometric and astrometric binaries, see the appendix!

@@

\section{Binarity and Stellar Rotation for $\delta$\,Lyr Cluster Members}

f15supp.pdf
